---
title: "First ARTMO LUT Inversion Simulations"
author: Mattia Rossi
output: html_document
---

This markdown is used for documenting the ARTMO simulations for LAI retrieval during my period at the IPL, LEO in 2018.
I separated the codes by simulation and added the code necessary to plot the results and to document strength and weaknesses of the simulation approach.
Each iteration will be calculated in the [R directory](https://github.com/mattia6690/ARTMO_R/tree/master/R) of this repository. The visualization and discussion of the results will be done within the [Documentation directory](https://github.com/mattia6690/ARTMO_R/tree/master/R) sparsed across diverse RMarkdowns

## Setup of Environment
```{r}

```


ARTMOdir<-"K:/SentinelVegetationProducts/S2_LAI"
ARTMOdir.ss<-paste0(ARTMOdir,"/Subsets")
ARTMOdir.in<-paste0(ARTMOdir,"/ARTMO_Inversion")


## First simulation

The first model I tried has the following specs:
* PROSAIL LUT inversion
* N 0-3 by 1 
* Chl 0-100 by 10
* LAI 0-8 by 0.1
* Angle 20-90 by 25
* 30000 Simulations
* 10 S-2 bands. All bands resampled to 10 m and the 60m band is excluded
* 
* Exponential COST Function with 1 sample: RMSE: 1.1 and R^[2] of around 0-8. The second best COST function is by the RMSE function:

```{r setup, include=FALSE}
directory<- "2509_Prosail_Inversion_30000_10Bands_v1"
```
